\documentclass[../report/main.tex]{subfiles}
 
\begin{document}

% The asterix after \subsection disables section numbering
\subsection*{Problem 1 Part A Problem Statement}
Determine the number of refrigerators to be shipped from plants to warehouses, and then warehouses to retailers to minimize the cost.

\subsection*{Problem 1 Part A Solution}
\begin{itemize}
	\item In all 1000 units will travel through the network at a minimum cost of \$17100.
	\newline
	\item Ship 150 units from plant \#1 to warehouse \#1 at a cost of \$1500.
	\item Ship 200 units from plant \#2 to warehouse \#1 at a cost of \$2200.
	\item Ship 250 units from plant \#2 to warehouse \#2 at a cost of \$2000.
	\item Ship 150 units from plant \#3 to warehouse \#2 at a cost of \$1200.
	\item Ship 100 units from plant \#3 to warehouse \#3 at a cost of \$ 900.
	\item Ship 150 units from plant \#4 to warehouse \#3 at a cost of \$1200.
	\newline
	\item Ship 100 units from warehouse \#1 to retailer \#1 at a cost of \$ 500.
	\item Ship 150 units from warehouse \#1 to retailer \#2 at a cost of \$ 900.
	\item Ship 100 units from warehouse \#1 to retailer \#3 at a cost of \$ 700.
	\item Ship 200 units from warehouse \#2 to retailer \#4 at a cost of \$1600.
	\item Ship 200 units from warehouse \#2 to retailer \#5 at a cost of \$2000.
	\item Ship 150 units from warehouse \#3 to retailer \#6 at a cost of \$1800.
	\item Ship 100 units from warehouse \#3 to retailer \#7 at a cost of \$ 600.
	\newline
	\item 150 total units will leave plant \#1 (capacity is 150).
	\item 450 total units will leave plant \#2 (capacity is 450).
	\item 250 total units will leave plant \#3 (capacity is 250).
	\item 150 total units will leave plant \#4 (capacity is 150).
	\newline
	\item 350 total units will enter warehouse \#1, 350 units will leave.
	\item 400 total units will enter warehouse \#2, 400 units will leave.
	\item 250 total units will enter warehouse \#3, 250 units will leave.
	\newline
	\item 100 total units will enter retailer \#1 (demand is 100).
	\item 150 total units will enter retailer \#2 (demand is 150).
	\item 100 total units will enter retailer \#3 (demand is 100).
	\item 200 total units will enter retailer \#4 (demand is 200).
	\item 200 total units will enter retailer \#5 (demand is 200).
	\item 150 total units will enter retailer \#6 (demand is 150).
	\item 100 total units will enter retailer \#7 (demand is 100).
\end{itemize}
\subsection*{Problem 1 Part A Linear Program Formulation}
\begin{enumerate}[1.]
	\item Overall idea of problem
	\begin{itemize}
		\item Refrigerators moving from $n=4$ plants to $q=3$ warehouses to $m=7$ retailers.
		\item Not all plants deliver to all warehouses.
		\item Not all warehouses deliver to all retailers.
		\item Costs of shipping from plants to warehouses vary by pair.
		\item Costs of shipping from warehouses to retailers vary by pair.
		\item Each plant has a capacity in terms of number of refrigerators it can supply.
		\item Each retailer has a capacity in terms of number of refrigerators it demands.
	\end{itemize}
	\item What is the goal?  What are you trying to achieve?
	\begin{itemize}
		\item Determine optimal shipping routes ($n$ to $q$ and $q$ to $m$).
		\item Determine number of refrigerators moving along each route ($n$ to $q$ and $q$ to $m$).
		\item Satisfy the demand of the retailers.
		\item Minimize the cost.
	\end{itemize}
	\item Identify variables
	\begin{itemize}
		\item $cp_{ij}$ = cost of moving a refrigerator between plant i and warehouse j
		\begin{itemize}
			\item   ex. $cp_{32} = 8$ = cost of moving from plant 3 to warehouse 2
			\item   9 variables
		\end{itemize}
		\item $cw_{jk}$ = cost of moving a refrigerator between warehouse j and retailer k
		\begin{itemize}
  			\item  ex. $cp_{14} = 10$ = cost of moving from warehouse 1 to retailer 4
  			\item  12 variables
		\end{itemize}
		\item $s_i$ = capacity (supply) of each plant
		\begin{itemize}
 			\item   ex. $s_2 = 450$ = number of refrigerators that plant 2 can supply
			\item    4 variables
		\end{itemize}
		\item $d_k$ = capacity (demand) of each retailer
		\begin{itemize}
			\item    ex. $d_6 = 150$ = number of refrigerators that plant 6 demands
			\item    7 variables
		\end{itemize}
		\item $np_{ij}$ = number of refrigerators shipped from plant i to warehouse j
		\begin{itemize}
			\item    9 variables
		\end{itemize}
		\item $nw_{jk}$ = number of refrigerators shipped from warehouse j to retailer k
		\begin{itemize}
			\item    12 variables
		\end{itemize}
	\end{itemize}
	\item Identify constraints
	\begin{itemize}
		\item $s_1 \leq 150$
		\item $s_2 \leq 450$
		\item $s_3 \leq 250$
		\item $s_4 \leq 150$
		\item $d_1 \geq 100$
		\item $d_2 \geq 150$
		\item $d_3 \geq 100$
		\item $d_4 \geq 200$
		\item $d_5 \geq 200$
		\item $d_6 \geq 150$
		\item $d_7 \geq 100$
		\item $np_{11} + np_{21} + np_{31}        = nw_{11} + nw_{12} + nw_{13} + nw_{14}$
		\item $np_{12} + np_{22} + np_{32} + np_{42} =               nw_{23} + nw_{24} + nw_{25} + nw_{26}$
		\item $              np_{33} + np_{43} =                      nw_{34} + nw_{35} + nw_{36} + nw_{37}$
		\item $s_1 = np_{11} + np_{12}$
		\item $s_2 = np_{21} + np_{22}$
		\item $s_3 = np_{31} + np_{32} + np_{33}$
		\item $s_4 =        np_{42} + np_{43}$
		\item $d_1 = nw_{11}$
		\item $d_2 = nw_{12}$
		\item $d_3 = nw_{13} + nw_{23}$
		\item $d_4 = nw_{14} + nw_{24} + nw_{34}$
		\item $d_5 =        nw_{25} + nw_{35}$
		\item $d_6 =        nw_{26} + nw_{36}$
		\item $d_7 =                      nw_{37}$
		\item $np_{11} \geq 0$
		\item $np_{12} \geq 0$
		\item $np_{21} \geq 0$
		\item $np_{22} \geq 0$
		\item $np_{31} \geq 0$
		\item $np_{32} \geq 0$
		\item $np_{33} \geq 0$
		\item $np_{42} \geq 0$
		\item $np_{43} \geq 0$
		\item $nw_{11} \geq 0$
		\item $nw_{12} \geq 0$
		\item $nw_{13} \geq 0$
		\item $nw_{14} \geq 0$
		\item $nw_{23} \geq 0$
		\item $nw_{24} \geq 0$
		\item $nw_{25} \geq 0$
		\item $nw_{26} \geq 0$
		\item $nw_{34} \geq 0$
		\item $nw_{35} \geq 0$
		\item $nw_{36} \geq 0$
		\item $nw_{37} \geq 0$
	\end{itemize}
	\item Identify inputs and outputs that you can control
	\begin{itemize}
		\item $np_{ij}$
		\item $nw_{jk}$
		\item $cost$
	\end{itemize}
	\item Specify all quantities mathematically
	\begin{itemize}
		\item Many have been defined above already.  A few more will be added here.
		\item $cost$ = [sum of ($np_{ij}*cp_{ij}$) for all routes between plants and warehouses]
			+ [sum of ($nw_{jk}*cw_{jk}$) for all routes between warehoues and retailers]
		\item $cp_{11} = 10$
		\item $cp_{12} = 15$
		\item $cp_{21} = 11$
		\item $cp_{22} = 8$
		\item $cp_{31} = 13$
		\item $cp_{32} = 8$
		\item $cp_{33} = 9$
		\item $cp_{42} = 14$
		\item $cp_{43} = 8$
		\item $cw_{11} = 5$
		\item $cw_{12} = 6$
		\item $cw_{13} = 7$
		\item $cw_{14} = 10$
		\item $cw_{23} = 12$
		\item $cw_{24} = 8$
		\item $cw_{25} = 10$
		\item $cw_{26} = 14$
		\item $cw_{34} = 14$
		\item $cw_{35} = 12$
		\item $cw_{36} = 12$
		\item $cw_{37} = 6$
	\end{itemize}
	\item Check the model for completeness and correctness
	\begin{itemize}
	\item All variables are positive.
	\end{itemize}
\end{enumerate}
\subsection*{Problem 1 Part A Matlab Code}
\lstinputlisting{../problem_one/partA.m}
\end{document}